\large The Size Distribution of Firms and Industrial Water Pollution \\ A Quantitative Analysis of China

### 2019-10-07 Documentation/IMF_RES_Fall_2019.tex
slides updated

\title[Firm Size and Industrial Pollution]{\large The Size Distribution of Firms and Industrial Water Pollution \\ A Quantitative Analysis of China}
\author[Qi, Tang and Xi]{{Ji Qi} \inst{\star} \and {Xin Tang} \inst{\dagger} \and {Xican Xi} \inst{\ddagger}}
\institute[MEP \& IMF \& FDU]{
    \inst{\star} {Chinese Academy for Environmental Planning} \and
    \inst{\dagger} {International Monetary Fund} \and
    \inst{\ddagger} {Fudan University}}
\date[IMF (RES) Fall 2019]{\footnotesize{\today} \\ \scriptsize{The views expressed here are those of the authors and do not necessarily reflect the views of the CAEP and the IMF.}}

@@

\begin{frame}
\frametitle{Motivation}
\begin{itemize}
\itemsep=0.15in
    \item
    Rapid economic growth in China is paired with severe environmental consequences.
    \begin{itemize}
        \item
        Is pollution an inevitable consequence of growth or exacerbated by policy distortions and/or market inefficiencies?
    \end{itemize}
    \item
    We argue that misallocation across firms reduces output and amplifies industrial pollution by distorting the firm size distribution.
    \item
    \textit{\color{blue}Policy Implications}:
    \begin{itemize}
        \item
        Reducing the distortions firms face increases output while reducing pollution.
        \item
        Environmental regulations could amplify existing market distortions.
    \end{itemize}
    \item
    We believe that the findings of our paper could be generalized to
    \begin{itemize}
        \item air and solid waste pollution;
        \item the agricultural sector;
        \item other developing countries.
    \end{itemize}
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Intuition}
\begin{itemize}
\itemsep=0.15in
    \item
    \textit{\color{blue}Hypothesis}: Distortions $\rightarrow$ Size Distribution $\rightarrow$ Industrial Pollution.
    \begin{itemize}
    \itemsep=0.10in
        \item
        Larger firms have lower pollution intensity because they use cleaner production and treatment technologies.
        \item
        Distortions limit the expansion of productive firms in China.
        \item
        Compared to an economy with fewer distortions (e.g., the U.S.), less productive firms with higher pollution intensity are active.
        \item
        As a result, aggregate output is lower, but industrial pollution is higher.
    \end{itemize}
    \item
    Technique effect dominates scale effect.
    \item
    \textit{\color{blue}Significance}: Growth and environmental protection are not necessarily a trade-off.
\end{itemize}
\end{frame}

@@

\begin{frame}
\frametitle{Related Literature}
\begin{itemize}
\itemsep=0.15in
    \item
    Misallocation:
    \begin{itemize}
        \item
        Restuccia and Rogerson (2008), Guner et al. (2008), Hsieh and Klenow (2009).
        \item
        We consider both the output and pollution.
    \end{itemize}
    \item
    Economic Growth and Environment:
    \begin{itemize}
        \item
        Grossman and Krueger (1993, 1995), Copeland and Taylor (2004), Levinson (2009).
        \item
        Cherniwchan et al. (2017), Shapiro and Walker (2018).
        \item
        We focus on a theoretical interpretation behind the scale and technique effects.
    \end{itemize}
    \item
    Technology Adoption in Developing Countries:
    \begin{itemize}
        \item
        Parente and Prescott (1994, 1999), Bustos (2011), Acemoglu et al. (2012).
        \item
        We study the role of size and misallocation.
    \end{itemize}
    \item
    {\color{black}Industrial Pollution in China}£º
    \begin{itemize}
        \item
        Jiang et al. (2014), Kahn et al. (2015), Cai et al. (2016), Jia (2017).
        \item
        We emphasize the role of distortions and size distribution.
    \end{itemize}
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Outline}
\begin{itemize}
\itemsep=0.15in
    \item
    Empirical Evidence:
    \begin{itemize}
        \item Data
        \item Fact: Pollution Intensity
        \item Fact: Employment Distribution
    \end{itemize}
    \item
    The Model:
    \begin{itemize}
        \item Measuring Distortions
        \item Analytical Properties
    \end{itemize}
    \item
    Quantitative Results:
    \begin{itemize}
        \item Removing Distortions
        \item Tightening Regulations
    \end{itemize}
\end{itemize}
\end{frame}

@@

\begin{frame}
\frametitle{Data}
\framesubtitle{Data Sources}
\begin{itemize}
\itemsep=0.15in
    \item
    National General Survey of Pollution Sources (2007)
    \begin{itemize}
    \item
    Firm sales, emission, and treatment equipment.
    \end{itemize}
    \item
    China National Economic Census (2004)
    \begin{itemize}
    \item
    Firm sales, employment, labor compensation, and capital stock.
    \end{itemize}
    \item
    Statistics of U.S. Business (2004)
    \begin{itemize}
    \item
    Firm size distribution in the U.S.
    \end{itemize}
\end{itemize}
\end{frame}

\begin{frame}[label=datasource]
\frametitle{Data}
\framesubtitle{Measurement}
\begin{itemize}
\itemsep=0.15in
    \item
    We use Chemical Oxygen Demand (COD) as the main measure.
    \begin{itemize}
    \itemsep=0.10in
    \item More than 70\% of firms in our sample have positive COD emissions.
    \item COD emission is highly correlated with those of other pollutants.
    \item In the Paper industry, $\text{corr}(\text{NH}_4^+,\text{COD}) = 0.82$, and $\text{corr}(\text{BOD},\text{COD}) = 0.94$.
    \end{itemize}
    \item
    We focus on the 5 most polluting industries.
    \begin{itemize}
    \item They account for 77\% of total COD emission in China.
    \end{itemize}
    \item
    We focus on the key sources.
    \begin{itemize}
        \item For the polluting industries, they account for 90\% of the emissions, and 80\% of the production.
    \end{itemize}
\end{itemize}
\hyperlink{coddef}{\beamergotobutton{COD Definition}}
\hyperlink{pollutants}{\beamergotobutton{Pollutants}}
\end{frame}

@@

\begin{frame}[label=codreg]
\frametitle{Firm Size and Pollution Intensity}
\framesubtitle{Regression Results}
\begin{itemize}
\itemsep=0.15in
    \item
    Regression Specification:
    \begin{align*}
        \log (\text{COD}_i) = &\underset{(0.17)}{-3.75} + \underset{(0.01)}{0.63} \times \log (\text{Output}_i) + \mathbf{X}_i\gvec{\upgamma} + \varepsilon_i, \\
        & N = 29,019, R^2 = 0.41.
    \end{align*}
    \item
    $\mathbf{X}_i$ controls for sectors, provinces, and ownership rights.
    \begin{itemize}
        \item Pollution intensity does \rtext{not} vary systematically with \btext{ownership rights}.
    \end{itemize}
    \item
    As sales rise by 1\%, emission intensity drops by $(1-0.63) = 0.37\%$.
\end{itemize}
\end{frame}

\begin{frame}[label=treatment1]
\frametitle{Treatment Technologies and Firm Size}
\begin{itemize}
\itemsep=0.15in
    \item
    For the Paper industry:
    \begin{itemize}
    \item
    Treatment efficiency ($1 - \text{COD Emitted}/\text{COD Generated}$):
    \end{itemize}
\end{itemize}

@@

\begin{frame}[label=producttech]
%\small
\frametitle{Production Technologies and Firm Size}
\framesubtitle{Regression Results}
\begin{itemize}
\itemsep=0.15in
    \item
    Large firms also {\color{black}generate} less pollution conditional on treatment technology.
    \item
    Regression Specifications:
    \begin{align*}
        \text{Physical:}   \quad \log (\text{COD}_i) &= \underset{(0.40)}{-3.50} + \underset{(0.01)}{0.58} \times \log (\text{Sales}_i) + \mathbf{X}_i\gvec{\upgamma} + \epsilon_i, \\
        \text{Chemical:}   \quad \log (\text{COD}_i) &= \underset{(0.49)}{-4.59} + \underset{(0.01)}{0.77} \times \log (\text{Sales}_i) + \mathbf{X}_i\gvec{\upgamma} + \epsilon_i, \\
        \text{Biological:} \quad \log (\text{COD}_i) &= \underset{(0.20)}{-4.37} + \underset{(0.01)}{0.67} \times \log (\text{Sales}_i) + \mathbf{X}_i\gvec{\upgamma} + \epsilon_i.
    \end{align*}
\end{itemize}
%\hyperlink{treattech}{\beamergotobutton{Treatment Technology Choice}}
\end{frame}

@@

\begin{frame}[label=accounting]
\frametitle{Accounting Exercise}
\begin{itemize}
\itemsep=0.15in
    \item
    {\color{blue}Question:} How will the {\color{black}average pollution intensity} change if the {\color{black}size distribution} is mechanically changed to that in the U.S.?
    \begin{itemize}
    \itemsep=0.10in
        \item
        Production level is fixed.
        \item
        The relation between pollution intensity and firm size in China is used.
        \item
        It captures the \textit{Technique} effect while holding the \textit{Scale} effect constant.
    \end{itemize}
    \item
    {\color{blue}Answer:} Average pollution intensity would drop by 33\%.
\end{itemize}
\hyperlink{accountingrbst}{\beamergotobutton{Robustness}}
\end{frame}

@@

\subsection{Setup}
\begin{frame}
\frametitle{Overview of the Model}
\begin{itemize}
\itemsep=0.15in
    \item
    A two-sector model with perfect substitution between products.
    \item
    Each sector features a Lucas (1978) span-of-control model.
    \item
    Firms differ in productivity and pollution intensity.
    \item
    Firms can use treatment equipment to reduce emissions.
    \begin{itemize}
    \item The cost of treatment equipment is independent of firm size.
    \item There are penalties for not using clean technology.
    \end{itemize}
    \item
    Correlated distortions that increase with firm size (Restuccia and Rogerson, 2008).
    \begin{itemize}
    \item Domestic local protectionism, size-dependent tax treatments, etc.
    \end{itemize}
    \item
    {\color{black}Steady state} analysis.
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Household}
\begin{itemize}
\itemsep=0.15in
    \item
    A representative household with a continuum of members:
    \begin{equation*}
        \sum_{t=0}^{\infty} \beta^t U(C_t).
    \end{equation*}
    \item
    Each member is endowed with $z$ units of \btext{sector-specific} managerial talent.
    \begin{itemize}
        \item The CDFs are $G^c(z)$ and $G^d(z)$ with a common support $Z \triangleq [0,\overline{z}]$;
        \item $z$ is fixed once drawn.
        \item A fraction $\mu$ of members possess talent in the \btext{polluting} sector.
    \end{itemize}
    \item
    Members can only become entrepreneurs in their designated sector, but are free to enter both sectors as worker.
    \item
    The household owns all firms and capital in the economy.
\end{itemize}
\end{frame}

@@

\begin{frame}[label=firmset]
\frametitle{Which Distortion Matters?}
\framesubtitle{Identification Assumption}
\begin{itemize}
\itemsep=0.15in
    \item
    We use the variations in average factor products to measure these wedges (Hsieh and Klenow, 2009).
    \item
    Let {\color{blue}$\tau_{z_i}, \tau_{k_i}$} and {\color{blue}$\tau_{l_i}$} be the wedges firm $i$ faces on the product, capital and labor market, the problem of firm $i$ is
    \begin{equation*}
      \pi_i = \max_{k_i,l_i} \left\{ (1-\tau_{z_i}) z_i^{1-\gamma} (k_i^{\alpha} l_i^{1-\alpha})^{\gamma} - (1+\tau_{k_i})Rk_i - (1+\tau_{l_i})W l_i \right\}.
    \end{equation*}
    \item
    Assuming $\tau_{l_i} = 0$:
    \begin{align*}
        \frac{y_i}{l_i} &= \frac{W}{(1-\alpha) \gamma (1-\tau_{z_i})} \varpropto \frac{1}{1-\tau_{z_i}}, \\
        \frac{k_i}{l_i} &= \frac{\alpha}{1-\alpha} \cdot \frac{W}{(1+\tau_{k_i})R} \varpropto \frac{1}{1+\tau_{k_i}}.
    \end{align*}
\end{itemize}
\end{frame}

@@

\begin{frame}[label=firm_opt2]
\frametitle{Firm's Optimization}
\framesubtitle{Technology Adoption Decision}
\begin{itemize}
\itemsep=0.15in
    \item
    Difference in potential profits using different technologies:
    \begin{equation*}
        \pi_1^d(z) - \pi_0^d(z) = \frac{\xi (1-\gamma)}{(1-\alpha)\gamma} W l^d(z) - Rk_E.
    \end{equation*}
    \item
    There exists a threshold $z^E$ where firms switch technology.
    \begin{itemize}
    \itemsep=0.10in
        \item
        $z_E$ increases with $\xi$ and decreases with $k_E$.
        \item
        $z_E$ increases with $\tau_z$.
    \end{itemize}
\end{itemize}
\hyperlink{prop1}{\beamergotobutton{Graphical}}
\end{frame}

>>>>

\title[Firm Size and Industrial Pollution]{\large The Size Distribution of Firms and Industrial Water Pollution \\ A Quantitative Analysis of China}
\author[Qi, Tang and Xi]{{Ji Qi} \inst{\star} \and {Xin Tang} \inst{\dagger} \and {Xican Xi} \inst{\ddagger}}
\institute[MEP \& IMF \& FDU]{
    \inst{\star} {Chinese Academy for Environmental Planning} \and
    \inst{\dagger} {International Monetary Fund} \and
    \inst{\ddagger} {Fudan University}}
\date[IMF (RES) Fall 2019]{\footnotesize{\today} \\ \scriptsize{The views expressed here are those of the authors and do not necessarily reflect the views of the CAEP or the IMF.}}

@@

\begin{frame}
\frametitle{Motivation}
\begin{itemize}
\itemsep=0.15in
    \item
    Rapid economic growth in China is paired with severe environmental consequences.
    \begin{itemize}
        \item
        Is pollution an inevitable consequence of growth or exacerbated by policy distortions and/or market inefficiencies?
    \end{itemize}
    \item
    We argue that misallocation across firms reduces output and amplifies industrial pollution by distorting firm size distribution.
    \item
    \textit{\color{blue}Policy Implications}:
    \begin{itemize}
        \item
        Reducing the distortions firms face increases output while decrease pollution.
        \item
        Environmental regulations could amplify existing market distortions.
    \end{itemize}
    \item
    We believe that the findings of our paper could be generalized to
    \begin{itemize}
        \item air and solid waste pollution;
        \item the agricultural sector;
        \item other developing countries.
    \end{itemize}
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Intuition}
\begin{itemize}
\itemsep=0.15in
    \item
    \textit{\color{blue}Hypothesis}: Distortions $\rightarrow$ Size Distribution $\rightarrow$ Industrial Pollution.
    \begin{itemize}
    \itemsep=0.10in
        \item
        Larger firms have lower pollution intensity because they use cleaner production and treatment technologies.
        \item
        Distortions limit the expansion of productive firms in China.
        \item
        Compared to an economy with fewer distortions (e.g., the U.S.), less productive but more polluting firms survive.
        \item
        As a result, aggregate output is lower, but industrial pollution is higher.
    \end{itemize}
    \item
    Technique effect dominates scale effect.
    \item
    \textit{\color{blue}Significance}: Growth and environmental protection are not necessarily a trade-off.
\end{itemize}
\end{frame}

@@

\begin{frame}
\frametitle{Related Literature}
\begin{itemize}
\itemsep=0.15in
    \item
    Misallocation:
    \begin{itemize}
        \item
        Restuccia and Rogerson (2008), Guner et al. (2008), Hsieh and Klenow (2009).
        \item
        We consider both the output and pollution.
    \end{itemize}
    \item
    Economic Growth and Environment:
    \begin{itemize}
        \item
        Grossman and Krueger (1993, 1995), Copeland and Taylor (2004), Levinson (2009).
        \item
        Cherniwchan et al. (2017), Shapiro and Walker (2018).
        \item
        We focus on a theoretical interpretation behind the scale and technique effects.
    \end{itemize}
    \item
    Technology Adoption in Developing Countries:
    \begin{itemize}
        \item
        Parente and Prescott (1994, 1999), Bustos (2011), Acemoglu et al. (2012).
        \item
        We study the role of size and misallocation.
    \end{itemize}
    \item
    {\color{black}Industrial Pollution in China}£º
    \begin{itemize}
        \item
        Jiang et al. (2014), Kahn et al. (2015), Cai et al. (2016), Jia (2017).
        \item
        We emphasize the role of economic factors.
    \end{itemize}
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Outline}
\begin{itemize}
\itemsep=0.15in
    \item
    Empirical Evidence:
    \begin{itemize}
        \item Data
        \item Fact: Pollution Intensity
        \item Fact: Employment Distribution
    \end{itemize}
    \item
    The Model:
    \begin{itemize}
        \item Measuring Distortions
        \item Analytical Properties
    \end{itemize}
    \item
    Quantitative Results:
    \begin{itemize}
        \item Removing Distortions
        \item Strengthening Regulations
    \end{itemize}
\end{itemize}
\end{frame}

@@

\begin{frame}
\frametitle{Data}
\framesubtitle{Data Sources}
\begin{itemize}
\itemsep=0.15in
    \item
    National General Survey of Pollution Sources (2007)
    \begin{itemize}
    \item
    Firm output, emission and treatment equipment.
    \end{itemize}
    \item
    China National Economic Census (2004)
    \begin{itemize}
    \item
    Firm output, employment labor compensation, and capital stock.
    \end{itemize}
    \item
    Statistics of U.S. Business (2004)
    \begin{itemize}
    \item
    Firm size distribution in the U.S.
    \end{itemize}
\end{itemize}
\end{frame}

\begin{frame}[label=datasource]
\frametitle{Data}
\framesubtitle{Measurement}
\begin{itemize}
\itemsep=0.15in
    \item
    We use Chemical Oxygen Demand (COD) as the main measure.
    \begin{itemize}
    \itemsep=0.10in
    \item More than 70\% firms in our sample have positive COD emission.
    \item COD emission is highly correlated with those of other pollutants.
    \item In the Paper industry, $\text{corr}(\text{NH}_4^+,\text{COD}) = 0.82$, and $\text{corr}(\text{BOD},\text{COD}) = 0.94$.
    \end{itemize}
    \item
    We focus on the 5 most polluting industries.
    \begin{itemize}
    \item They account for 77\% of total COD emission in China.
    \end{itemize}
    \item
    We focus on the key sources.
    \begin{itemize}
        \item For the polluting industries, they account for 90\% of the emission and 80\% of the production.
    \end{itemize}
\end{itemize}
\hyperlink{coddef}{\beamergotobutton{COD Definition}}
\hyperlink{pollutants}{\beamergotobutton{Pollutants}}
\end{frame}

@@

\begin{frame}[label=codreg]
\frametitle{Firm Size and Pollution Intensity}
\framesubtitle{Regression Results}
\begin{itemize}
\itemsep=0.15in
    \item
    Regression Specification:
    \begin{align*}
        \log (\text{COD}_i) = &\underset{(0.17)}{-3.75} + \underset{(0.01)}{0.63} \times \log (\text{Output}_i) + \mathbf{X}_i\gvec{\upgamma} + \varepsilon_i, \\
        & N = 29,019, R^2 = 0.41.
    \end{align*}
    \item
    $\mathbf{X}_i$ controls for sectors, provinces and ownership rights.
    \begin{itemize}
        \item Pollution intensity does \rtext{not} vary systematically with \btext{ownership rights}.
    \end{itemize}
    \item
    As output rises by 1\%, emission intensity drops by $(1-0.63) = 0.37\%$.
\end{itemize}
\end{frame}

\begin{frame}[label=treatment1]
\frametitle{Treatment Technologies and Firm Size}
\begin{itemize}
\itemsep=0.15in
    \item
    Treatment efficiency: $1 - \text{COD Emitted}/\text{COD Generated}$.
    \begin{itemize}
    \item
    For the Paper industry:
    \end{itemize}
\end{itemize}

@@

\begin{frame}[label=producttech]
%\small
\frametitle{Production Technologies and Firm Size}
\framesubtitle{Regression Results}
\begin{itemize}
\itemsep=0.15in
    \item
    Large firms also {\color{black}generate} less pollution conditional on treatment technology.
    \item
    Regression Specifications:
    \begin{align*}
        \text{Physical:}   \quad \log (\text{COD}_i) &= \underset{(0.40)}{-3.50} + \underset{(0.01)}{0.58} \times \log (\text{Output}_i) + \mathbf{X}_i\gvec{\upgamma} + \epsilon_i, \\
        \text{Chemical:}   \quad \log (\text{COD}_i) &= \underset{(0.49)}{-4.59} + \underset{(0.01)}{0.77} \times \log (\text{Output}_i) + \mathbf{X}_i\gvec{\upgamma} + \epsilon_i, \\
        \text{Biological:} \quad \log (\text{COD}_i) &= \underset{(0.20)}{-4.37} + \underset{(0.01)}{0.67} \times \log (\text{Output}_i) + \mathbf{X}_i\gvec{\upgamma} + \epsilon_i.
    \end{align*}
\end{itemize}
%\hyperlink{treattech}{\beamergotobutton{Treatment Technology Choice}}
\end{frame}

@@

\begin{frame}[label=accounting]
\frametitle{Accounting Exercise}
\begin{itemize}
\itemsep=0.15in
    \item
    {\color{blue}Question:} How will {\color{black}average pollution intensity} change if the {\color{black}size distribution} is mechanically changed to that in the U.S.?
    \begin{itemize}
    \itemsep=0.10in
        \item
        Production level is fixed.
        \item
        The relation between pollution intensity and firm size in China is used.
        \item
        It captures the \textit{Technique Effect} while holding the \textit{Scale Effect} constant.
    \end{itemize}
    \item
    {\color{blue}Answer:} Average pollution intensity would drop by 33\%.
\end{itemize}
\hyperlink{accountingrbst}{\beamergotobutton{Robustness}}
\end{frame}

@@

\subsection{Setup}
\begin{frame}
\frametitle{Overview of the Model}
\begin{itemize}
\itemsep=0.15in
    \item
    A two-sector model with perfect substitution between products.
    \item
    Each sector features a Lucas (1978) span-of-control economy.
    \item
    Firms differ in productivity and pollution intensity.
    \item
    Firms can use treatment equipment to reduce emissions.
    \begin{itemize}
    \item The cost of treatment equipment is independent of firm size.
    \item There are penalties for not using clean technology.
    \end{itemize}
    \item
    Correlated distortions that increase with firm's productivity (Restuccia and Rogerson, 2008).
    \begin{itemize}
    \item Domestic local protectionism, size-dependent tax treatments, etc.
    \end{itemize}
    \item
    {\color{black}Steady state} analysis.
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Household}
\begin{itemize}
\itemsep=0.15in
    \item
    A representative household with a continuum of members:
    \begin{equation*}
        \sum_{t=0}^{\infty} \beta^t U(C_t).
    \end{equation*}
    \item
    Each member is endowed with $z$ units of \btext{sector-specific} managerial talent.
    \begin{itemize}
        \item The CDFs are $G^c(z)$ and $G^d(z)$ with a common support $Z \triangleq [0,\overline{z}]$;
        \item $z$ is fixed once drawn;
        \item A fraction $\mu$ of members possess talent in the \btext{polluting} sector.
    \end{itemize}
    \item
    Members can only become entrepreneurs in their designated sector, but are free to enter both sectors as worker.
    \item
    The household owns all firms and capital in the economy.
\end{itemize}
\end{frame}

@@

\begin{frame}[label=firmset]
\frametitle{Which Distortion Matters?}
\framesubtitle{Identification Assumption}
\begin{itemize}
\itemsep=0.15in
    \item
    Let {\color{blue}$\tau_{z_i}, \tau_{k_i}$} and {\color{blue}$\tau_{l_i}$} be the wedges firm $i$ faces on the product, capital and labor market, the problem of firm $i$ is
    \begin{equation*}
      \pi_i = \max_{k_i,l_i} \left\{ (1-\tau_{z_i}) z_i^{1-\gamma} (k_i^{\alpha} l_i^{1-\alpha})^{\gamma} - (1+\tau_{k_i})Rk_i - (1+\tau_{l_i})W l_i \right\}.
    \end{equation*}
    \item
    We use the variations in average factor products to measure these wedges (Hsieh and Klenow, 2009).    
    \item
    Assuming $\tau_{l_i} = 0$:
    \begin{align*}
        \frac{y_i}{l_i} &= \frac{W}{(1-\alpha) \gamma (1-\tau_{z_i})} \varpropto \frac{1}{1-\tau_{z_i}}, \\
        \frac{k_i}{l_i} &= \frac{\alpha}{1-\alpha} \cdot \frac{W}{(1+\tau_{k_i})R} \varpropto \frac{1}{1+\tau_{k_i}}.
    \end{align*}
\end{itemize}
\end{frame}

@@

\begin{frame}[label=firm_opt2]
\frametitle{Firm's Optimization}
\framesubtitle{Technology Adoption Decision}
\begin{itemize}
\itemsep=0.15in
    \item
    Difference in potential profits using different technologies:
    \begin{equation*}
        \pi_1^d(z) - \pi_0^d(z) = \frac{\xi (1-\gamma)}{(1-\alpha)\gamma} W l^d(z) - Rk_E.
    \end{equation*}
    \item
    There exists a threshold $z^E$ where firms switch technology.
    \begin{itemize}
    \itemsep=0.10in
        \item
        $z_E$ decreases with $\xi$ and increases with $k_E$.
        \item
        $z_E$ increases with $\tau_z$.
    \end{itemize}
\end{itemize}
\hyperlink{prop1}{\beamergotobutton{Graphical}}
\end{frame}
